---
title: "P8105_hw5_wz2630"
output: github_document
date: 2023-11-15
---
```{r message=FALSE, warning=FALSE}
# Intall packages
library(tidyverse)
library(readr)
library(purrr)
library(ggplot2)

```

## Problem 1 
(not graded)


## Problem 2

Longitudinal study 

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:
```{r}

data_files = tibble(filename = list.files("./data/"))
# csv files I want to read in

read_csv = function(csv, path = "./data/") {
  paste(path, csv, sep = "/") |> 
  read.csv()
}
# create function for reading csv files

longitudinal_study =  
  data_files |> 
  mutate(nested_data = map(data_files$filename, read_csv)) |> 
  #list of datasets to apply read_csv function to
  unnest(nested_data) |> 
  #unnests data into all 8 columns
  mutate(arm_subject = map_chr(.x = filename, ~ unlist(str_split(.x, "\\.") ) [[1]] )) |> 
  #create new column to rename subjects by splitting with '.' and using only the first part
  mutate(arm = map_chr(.x = arm_subject, ~ unlist(str_split(.x, "_") ) [[1]] )) |> 
  mutate(subject_id = map_chr(.x = arm_subject, ~ unlist(str_split(.x, "_") ) [[2]] )) |> 
  #separate into arm and subject id columns
  select(-filename, -arm_subject)
  #only keep necessary columns of tidy dataset
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.
```{r}
#pivot longer data in order to create graph over time
pivot_longer = 
  longitudinal_study |> 
  pivot_longer(week_1:week_8,
               names_to = "week",
               names_prefix = "week_", #removes the week prefix in the week values
               values_to = "value") |> 
  mutate(week = as.integer(week))

spaghetti_plot = 
  pivot_longer |> 
  ggplot(aes(week, value, color = subject_id)) + 
  geom_line() + 
  facet_wrap(~arm) + 
  theme(legend.position = "bottom") +
  labs(x = 'Week', 
       y = 'Value', 
       title = 'Spaghetti Plot',
       color = "Subject ID")

spaghetti_plot
```

**Comments:**

Since we are asked to compare between the 2 groups, I applied facet_wrap to better visualize it. The control arm have overall lower values throughout the 8 weeks as compared to the experimental arm. There seems to be an increasing trend in the experimental arm as time passes.



## Problem 3

Simulation to explore power in a one-sample t-test

* Fix n=30
* Fix σ=5

```{r}
set.seed(123)

sim_t_test = function(n, mu = 0, sigma = 5) {
  
    sim_data = tibble( x = rnorm(n, mean = mu, sd = sigma))
    
    t_test_output = broom::tidy(t.test(sim_data))

    t_test_output |> 
      select(estimate, p.value)
}

t_test_output = tibble(
  sample_size = 30,
  iter = 1:5000
) |>
  mutate(estimate_t_test = map(sample_size, sim_t_test)) |>
  unnest(estimate_t_test)
```

Repeat the above for μ={1,2,3,4,5,6}
```{r}
set.seed(12)

sim_t_test = function(n, mu, sigma = 5) {
  
    sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma)
    )
    
    t_test_output = broom::tidy(t.test(sim_data))

    t_test_output |> 
      select(estimate, p.value)
}

t_test_output_2 = expand_grid(
  mu_value = c(1, 2, 3, 4, 5, 6),
  sample_size = 30,
  iter = 1:5000
) |>
  mutate(estimate_t = map(mu_value, ~sim_t_test(n = sample_size, mu = .))) |>
  unnest(estimate_t)
```

**(a)** Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.
```{r}

```









